\subsection{Conversation Worker}

The conversation-worker is responsible for taking in a sentence, usually from the
transcript-worker and converting into an tuple $<I, E>$ where $I$ is the intent and
$E$ is our entities. An intent for our purposes is an action to take within our system.
The entities then are the elements that make up that action. For example, given the
sentence ``Move block A onto block B'', intent would be ``move'' with the entities being
``block A'' and ``block B''.

For our implementation of this component, we utilize the Watson Assistant service. Within this
service, we define intents, and then provide example sentences that would fit that intent
to train the system. This has the benefit of allowing the system the capacity to handle slightly
differently worded sentences than what we might expect, as well as gloss over spelling and
grammatical errors that arise from the transcription process. For entities, we utilize built-in
system ones (such as numbers), as well as define our own, where then entities are largely detected
through from the input sentence using simple pattern matching. For this system, we
pre-build our worker with a list of intents and entities for a given domain, but also
allow on-the-fly training by users through mechanisms like Reagent, as explored in
Chapter~\ref{chap:reagent} The Watson Assistant service also provides a mechanism
for designing and constructing dialog trees that such a system could follow, however, we
do not use this service, relying instead on planning algorithms, to better handle multi-modal
input and intent resolution related to it.
