\subsection{spatial-context-bridge}

% TODO: smoothing on x,y coordinate. cite to $1 filter paper.

The spatial-context-bridge provides a generic mapping interface to unify different pointing
devices, such as kinect or cellphones. At its core, it takes relatively raw information about
the action, and maps it onto what the mouse equivalent would be, and the appropriate place
on the screen to place that action. For any input mechanism, we expect to receive a raw
X,Y coordinate as it corresponds to the overall display-worker's X,Y coordinates. This X,Y
coordinate is then translated down into a relative X,Y coordinate by examining through the
open webviews, iterating down the z-index of the display-worker, such that the top displayed
webviews are examined, going down the line, before looking at webviews that may be stacked
upon. Through this mechanism, we are guaranteed to get the topmost webview for a given X,Y
coordinate, regardless of the level of stacking that might exist. From there, we provide
additional transformations depending on the input source. For example, the input from
kinect system is in terms of hand orientation, where for one hand, be it right or left, it
can then be either pointing, open, or closed. An open, closed, open action sequence is
then translated into a singular mouse click, with smoothing applied to action inputs to
prevent toggling caused by jitters. For example, we may expect that when a user closes
their hand, the kinect system may report a closed hand relatively stably, but have brief
frames where the hand is detected as open. These frames last only for a few frames per
second before going back to being detected as closed once again. The spatial-context-bridge
provides mechanisms to handle this case, and leave the hand as closed, freeing the
developer of the underlying system from implementing this behavior themselves. This also
has the added benefit wherein calibration in some sense can be done within this module
and applied immediately to new input mechanisms without the developer of said input
mechanism having to be involved.
