\section{Prior Work}

Planning, and more specifically plan recognition, is a rich field of
research that has a broad range of prior work that we draw from. For planning,
one branch of work is ``deductive planning'', wherein given a goal and a series 
of axioms,
the resulting proof gives a plan structure~\cite{green_application_1969}. This
approach is attractive as it allows the usage of first-order logic to define
our world, and the state transitions. Further work was done to handle concepts
of conditional branching, plan composition, and 
recursion~\cite{metzing_plan_1989,biundo_deductive_1992,rosenschein_plan_1981}.
However, through the regular use of FOL, we see a larger potential of ending
up with side-effects of actions, which can be undesirable for planning. An
alternative concept is through the usage of STRIPS-style 
planners~\cite{fikes_strips_1971}. Within these planners, each action is
defined via a complete structure with pre-conditions and post-conditions for
each action. This approach is attractive as it provides a useful mechanism for
dealing with the framing problem~\cite{mccarthy_philosophical_1969}. However,
these planners generally utilize a predicate calculus that lacks the full
expressiveness of first-order logic, not to mention higher order logics like
the \CEC. While STRIPS-styles planners work well across many domains, they
rely on deterministic planning. Extending the concept, conditional nonlinear
planners~\cite{peot_conditional_1992} and partial 
planners~\cite{pryor_planning_1996}
provide a mechanism for dealing with non-deterministic plans through if-else
like structures. While we do make usage of elements of these planners for
intent resolution, we avoid bringing in a full-on non-deterministic planner
so as to avoid the increased complexity and potential combinatorial explosion
of states as to do would also call for a limitation on the
expressivity~\cite{rintanen_constructing_1999}. As such, we also do
not concern ourselves with other extensions to classical planners such as 
probabilistic 
planners~\cite{boutilier_decision-theoretic_1999,kaelbling_planning_1998}.
It should be noted that many of these planners operate at a level below
first-order logic which helps to limit complexity, and is actively suitable
for purely about actions in the world and only their physical effects. For
our needs where we look to handle the \CEC, which operates at a level
\emph{above} first-order, we then need additional machinery.

We now examine applications of planners to related domain as us,
namely in operating over mental states of agents in group environments.
For example, work in human-robot teaming has focused on
the use of planning techniques that take human goals and
mental states into account~\cite{briggs_multi-modal_2012}.
In addition, work on human-aware task planning for mobile robots
\cite{cirillo_human-aware_2009} has used \emph{predicted} plans of humans to
guide the system's own planning.
\cite{talamadupula_coordination_2014,chakraborti_planning_2015} showed this
approach more explicitly, representing and reasoning over a subset
of the humans' mental states relevant to the autonomous system's planning
problems.
Recent work has adapted these ideas to proactive decision making
\cite{sengupta_radar_2017,kim_towards_2017} and smart-room environments
\cite{chakraborti_mr._2017}. However, in these cases, an agent's belief
is implied, but that under the hood, states are represented in a less
expressive formalization. \cite{pearce_etal_social_planning_aaai2014}
note the importance of what they call ``social planning,'' which
includes an agent achieving a goal via the modification of the mental
states of others. Indeed, they include nested belief operators, but
their scope does not include unrestricted quantification, rather
sub-formulae in zero-order logic; and the other intensional operators,
epistemic and otherwise, are absent.
