%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%                                                                 %
%                         ACKNOWLEDGEMENT                         %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 
\specialhead{ACKNOWLEDGMENT}
 
I would like to thank my advisor Prof. Selmer Bringsjord for his immense help, support, and guidance
that he has provided me over the years. I would like to additionally thank Dr. Hui Su for his
role as director of the Cognitive and Immersive Systems Lab (CISL) which has funded my work, and driven
my research projects. I thank my committee members Prof. Carlos Varela, Prof. Bolek Szymanski, and
Dr. Jeffery O. Kephart for their support in helping me to refine and extend my research vision. My
labmates at CISL have been very helpful to me over the years in creating use-cases for my work,
and for provding useful sounding boards to my work. Finally, I would like to thank the support
staff of RPI who have been extremely helpful everytime I've needed them, be it in tracking down
people, getting forms dealt with, or the other miscellaneous tasks one deals with in pursuing a
PhD. Of these people, I would give special mention to Terry Hayden and Paula Monahan.

I would like to acknowledge the help and support of my family and friends through the years.
My parents have patiently guided me over the years, lending advice and support as needed, while
being wise enough to leave me to make my own mistakes and learn from them. To my friends Dr. Daniel
Eckhardt and Jeramey Tyler, thank you for being sounding boards to the turmoils of graduate school
and life in general.

I am grateful for the support of IBM who has funded my work and the CISL at large over the
course of my doctoral studies. In setting up the AI Horizons Network and running a yearly
colloquium to connect researchers across a number of universities and internal to IBM, it has
lead to fruitful collaborations and lively discussions. Additionally, I thank ASOFR and ONR
for their support as part of my work early work.