\subsection{Surveys}

For the experiment, participants were asked to fill out a pre- and
post-survey. The pre-survey asked for familiarity with smart
room environments and then asked for familiarity with the
following devices:

\begin{itemize}
    \item Wiimote
    \item Kinect
    \item Bluetooth Pointer
    \item Mouse
    \item Trackpad
    \item Laser Pointer
    \item Cellphone with attached pointer hardware
    \item Cellphone with attached reflective panels (like VICON)
    \item Cellphone with no additional hardware
\end{itemize}

The post-survey utilized the NASA Task Load 
Index~\cite{hart_development_1988} which asks users to rank
from ``Very Low'' to ``very High'' a range of topics which were:

\begin{itemize}
    \item \textbf{Mental Demand} - How mentally demanding was the task?
    \item \textbf{Physical Demand} - How physically demanding was the task?
    \item \textbf{Temporal Demand} - How hurried or rushed was the pace of the task?
    \item \textbf{Performance} - How successful were you in accomplishing what
you were asked to do?
    \item \textbf{Effort} - How hard did you have to work to accomplish
your level of performance?
    \item \textbf{Frustration} - How insecure, discouraged, irritated, stressed,
and annoyed were you?
\end{itemize}

In addition to the above, participants were given an open-ended
box to fill in any other comments they might have about the system.
During the experiment, researchers took a number of observational
comments about the participant.